---
title: "Classification of Breast Cancer condition"
author: "Ranu Sharma"
date: "10/28/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of breast cancer condition in 570 samples and 32 features

Features describe characteristics of the cell nuclei present in the image.

This database is also can be found on UCI Machine Learning Repository: <https://archive.ics.uci.edu/ml/datasets/Breast+Cancer+Wisconsin+%28Diagnostic%29>

Attribute Information:

1) ID number 2) Diagnosis (M = malignant, B = benign) 3-32)

Ten real-valued features are computed for each cell nucleus:

a) radius (mean of distances from center to points on the perimeter) b) texture (standard deviation of gray-scale values) c) perimeter d) area e) smoothness (local variation in radius lengths) f) compactness (perimeter^2 / area - 1.0) g) concavity (severity of concave portions of the contour) h) concave points (number of concave portions of the contour) i) symmetry j) fractal dimension ("coastline approximation" - 1)

The mean, standard error and "worst" or largest (mean of the three largest values) of these features were computed for each image, resulting in 30 features. For instance, field 3 is Mean Radius, field 13 is Radius SE, field 23 is Worst Radius.

All feature values are recoded with four significant digits.

Missing attribute values: none

Class distribution: **357 benign, 212 malignant**

## Loading libraries

```{r libraries, echo=FALSE}
library(ggplot2) 
library(tibble)
library(readr)
library(data.table)
library(Hmisc)
library(plyr)
library(dplyr)
library(caret)
library(caretEnsemble)
library(ggthemes)
library(scales)
library(MLmetrics)
library(gbm)
```

```{r pressure}
data <- read.csv("/Users/vimal/Machine-learning/breast_cancer/data.csv")
```

```{r file load}
str(data)
data <- data %>% select(-X)
data %>% as.tibble()
```

##Pre-processing
*Finding NA values*
```{r NA find}
any(is.na(data)) 
```

*Centering and scaling numerical columns*
```{r normalization}
preProcValues <- preProcess(data, method = c("BoxCox", "center", "scale", "spatialSign"))
train_processed <- predict(preProcValues, data)
```

*Converting outcome variable to numeric*
```{r editing1}
train_processed$diagnosis<-ifelse(train_processed$diagnosis=='M',0,1)
str(train_processed)
```

*Converting the dependent variable back to categorical*
```{r editing2}
train_processed$diagnosis<-as.factor(train_processed$diagnosis)
```

*Spliting training set into two parts based on outcome: 75% and 25%*
```{r data splitting}
index <- createDataPartition(train_processed$diagnosis, p=0.75, list=FALSE)
trainSet <- train_processed[ index,]
testSet <- train_processed[-index,]
```

*Checking the structure of trainSet & testSet*
```{r data structure}
str(trainSet)
str(testSet)
```

*Feature selection using rfe in caret*
```{r feature selection}
control <- rfeControl(functions = rfFuncs,
                      method = "repeatedcv",
                      repeats = 3,
                      verbose = FALSE)
outcomeName<-'diagnosis'
predictors<-names(trainSet)[!names(trainSet) %in% outcomeName]
Diagnosis_Pred_Profile <- rfe(trainSet[,predictors], trainSet[,outcomeName],
                         rfeControl = control)
Diagnosis_Pred_Profile

predictors<-c("perimeter_worst", "concave.points_worst", "area_worst", "radius_worst", "texture_worst")
```

##Model building
*Gradient boosting*
```{r gradient boost model building}
fitControl <- trainControl(method = "repeatedcv", number = 5, repeats = 5)

model_gbm<-train(trainSet[,predictors],trainSet[,outcomeName],method='gbm',trControl=fitControl,tuneLength=10)
model_gbm_all_features<-train(trainSet[,2:31],trainSet[,outcomeName],method='gbm',trControl=fitControl,tuneLength=10)

plot(model_gbm)

varImp(object=model_gbm)
plot(varImp(object=model_gbm),main="GBM - Variable Importance")

predictions1<-predict.train(object=model_gbm,testSet[,predictors],type="raw")
table(predictions1)
confusionMatrix(predictions1,testSet[,outcomeName])
```

##SVM model building
```{r svm model building}
fitcontrol <- trainControl(method="repeatedcv", number=10, repeats=3)
metric <- "Accuracy"
levels(trainSet$diagnosis) <- c("Malignant", "Benign")
levels(testSet$diagnosis) <- c("Malignant", "Benign")

svm_fit <- train(trainSet[,predictors],trainSet[,outcomeName], 
                     data=trainSet, 
                     method = "svmRadial", 
                     trControl = fitControl, 
                     preProc = c("center", "scale"),
                     tuneLength = 8,
                     metric = metric)

predictions_svm<-predict.train(object=svm_fit,testSet[,predictors])
Accuracy(predictions_svm, testSet$diagnosis)
table(predictions_svm)
confusionMatrix(predictions_svm,testSet$diagnosis)
```